Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-16 manuscript/ERL_global_C_SI.Rmd
cropped figures & adjusted size for fit on one page
Update ERL_global_C_SI.Rmd

#C cycle diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/C_cycle_diagrams/", full.names = TRUE))) # first remove old files

#flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/", full.names = TRUE)
#file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/C_cycle_diagrams/")

#Age diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/age_trends/", full.names = TRUE))) # first remove old files

#flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForC-db/ForC/figures/age_trends/", full.names = TRUE)
#file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/tables_figures/age_trends/")

@@

\blandscape
## Figure `r diagram_TrB_young`. C cycle diagram for young tropical broadleaf forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = "C cycle diagram for young tropical broadleaf forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='90%', fig.pos='H'}

@@

## Figure `r diagram_TeB_young`. C cycle diagram for young temperate broadleaf forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = "C cycle diagram for young temperate broadleaf forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='90%', fig.pos='H'}

@@

## Figure `r diagram_TeN_young`. C cycle diagram for young temperate conifer forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = " C cycle diagram for young temperate conifer forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='90%', fig.pos='H'}

@@

## Figure `r diagram_BoN_young`. C cycle diagram for young boreal conifer forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = "C cycle diagram for young boreal conifer forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='90%', fig.pos='H'}

>>>>

#C cycle diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/manuscript/tables_figures/C_cycle_diagrams/", full.names = TRUE))) # first remove old files

#flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/", full.names = TRUE)
#file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/manuscript/tables_figures/C_cycle_diagrams/")

#Age diagrams
#do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/manuscript/tables_figures/age_trends/", full.names = TRUE))) # first remove old files

#flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForC-db/ForC/figures/age_trends/", full.names = TRUE)
#file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ERL-review/manuscript/tables_figures/age_trends/")

@@

\blandscape
## Figure `r diagram_TrB_young`. C cycle diagram for young tropical broadleaf forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = "C cycle diagram for young tropical broadleaf forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='87%', fig.pos='H'}

@@

## Figure `r diagram_TeB_young`. C cycle diagram for young temperate broadleaf forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = "C cycle diagram for young temperate broadleaf forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='87%', fig.pos='H'}

@@

## Figure `r diagram_TeN_young`. C cycle diagram for young temperate conifer forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = " C cycle diagram for young temperate conifer forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='87%', fig.pos='H'}

@@

## Figure `r diagram_BoN_young`. C cycle diagram for young boreal conifer forests.
```{r eval = TRUE, echo=FALSE, fig.align = "center", fig.cap = "C cycle diagram for young boreal conifer forests. Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are observed ranges, where geographically distinct areas are treated as the unit of replication. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$ (stocks). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow size is proportional to the square root of corresponding flux.", out.width='87%', fig.pos='H'}
